Robotic Cart System

### 2021-05-01 parts/10-introduction.tex
Final report updates
Initial feedback from Dr. Miah

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are costlier than they are worth.

@@

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------
Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}. Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organized into six chapters:

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

>>>>

\todo[inline]{Please see the introduction chapter of one of my senior project
  reports at \url{http://ee.bradley.edu/projects/proj2017/ekf_slam/Downloads/seniorProject_finalReport.pdf}}

\todo[inline]{The idea is to write everything you talked about in your final
  presentation from slide 5- 11}

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organized into six chapters:
\todo[inline]{This section should go at the end of the chapter.}

%----------------------------------------------------------------------
\section{Motivation and Problem Statement}
%----------------------------------------------------------------------
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are more costly than they are worth.

@@

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------

\todo[inline]{In this section, include all the figures from the final
  presentation! You will need to write the explanation of each of the existing 
  mobile carts (you already talked about it during your presentation)}

Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}. Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:

### 2021-05-01 parts/20-system_architecture.tex
Initial feedback from Dr. Miah

%----------------------------------------------------------------------
\section{System Block Diagram}
%----------------------------------------------------------------------
The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in Fig. \ref{fig:sys_block_diag}. The proposed smart robotic cart is a wheeled robot that sends and receives radio signals to follow the remote target which acts as the beacon for the robotic cart system.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
    \caption{System level block diagram detailing inputs and outputs to the
      robotic cart system.}
	\label{fig:sys_block_diag}
\end{figure}

%----------------------------------------------------------------------
\section{Subsystem Block Diagrams}
%----------------------------------------------------------------------
The Mobile Cart and the Remote Target subsystems are two separate operations within the robotic cart system that run simultaneously. The two subsystems communicate with one another by relaying radio messages between them. The first block diagram is of the Remote Target subsystem shown in Fig. \ref{fig:remote_block_diag}. Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4V Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts. The two inputs for this system are the battery power and the incoming RF messages which are passed through the RF transceiver Module and output the outgoing RF messages.

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{figs/img/remoteBlockDiagram.png}
  \caption{Remote Target block diagram}
  \label{fig:remote_block_diag}
\end{figure}

\vspace*{12pt}
\noindent
The Mobile Cart subsystem block diagram, shown in Fig. \ref{fig:mobile_block_diag}, is the most complex of the two subsystems. The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue). The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart. The final input to the mobile cart subsystem is the incoming RF signals. These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer. The dual-direction multiplexer then takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer. Once the embedded computer gets these signals it can calculate the localization and navigation algorithms and pass the information to the DC motors.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
  \label{fig:mobile_block_diag}
\end{figure}

%----------------------------------------------------------------------
\section{System Components}
%----------------------------------------------------------------------
There are several components that are required for the mobile cart system. Although some of these parts are available in the Bradley University laboratory, other parts must be purchased. The parts that exist in the lab are listed in \autoref{tab:Partslablist}. Also, Fig. \ref{tab:Partslist} shows the list of parts that were purchased. The parts compiled in the lists are the required parts needed to build two smart robotic cart systems.

@@

\vspace*{12pt}
\noindent
The reflector array will be mounted on top of the cart with a stepper motor. There are two reflector designs that were evaluated in this project. The first, shown in Fig. \ref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of the signals that come into the reflector perpendicularly. Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array. The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this.

\vspace*{12pt}
\noindent
To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in Fig. \ref{fig:parabolicReflector1}. The lower half of this reflector is paraboloidal in shape to limit the signals coming from below. The upper part of the reflector is strictly parabolic. This shape focuses the signals in the horizontal plane, but allows signals from above to still be received. The plan is to construct both of these reflector designs by 3D printing the frames, then lining them with reflective foil tape. Both models will then be tested to determine which design works better.

\begin{figure}[h!]
  \centering
  \begin{minipage}[t]{0.5\textwidth}
    \centering
    \includegraphics[height=2in]{figs/img/paraboloidalReflector}
    \captionsetup{width=\textwidth, justification=raggedright}
    \caption{Paraboloidal Reflector Model}
    \label{fig:parabolodialReflector}
  \end{minipage}
  \begin{minipage}[t]{0.4\textwidth}
    \centering
    \includegraphics[height=2in]{figs/img/parabolicReflector}
    \captionsetup{width=\textwidth, justification=raggedright}
    \caption{Combined Parabolic/Paraboloidal Reflector}
    \label{fig:parabolicReflector1}
  \end{minipage}
\end{figure}

>>>>

%----------------------------------------------------------------------
\section{System Block Diagram}
%----------------------------------------------------------------------
The overall system architecture of this project consists of two subsystems which
are the Mobile Cart and the Remote Target, which is held by the user or
customer, as shown in Fig. \ref{fig:sys_block_diag}. The proposed smart robotic
cart is a wheeled robot that sends and receives radio signals to follow the
remote target which acts as the beacon for the robotic cart system. %
%
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
  \caption{System level block diagram detailing inputs and outputs to the
    robotic cart system.}
	\label{fig:sys_block_diag}
\end{figure}
%

@@

%----------------------------------------------------------------------
\section{Subsystem Block Diagrams}
%----------------------------------------------------------------------
The Mobile Cart and the Remote Target subsystems are two separate operations
within the robotic cart system that run simultaneously. The two subsystems
communicate with one another by relaying radio messages between them. The first
block diagram is of the Remote Target subsystem shown in Fig.
\ref{fig:remote_block_diag}. Of the two subsystems the Remote Target is the
simplest since it only requires an XBee module attached to a 7.4V Li-Po battery
with a voltage regulation circuit since the XBee has a smaller input voltage of
3.3 volts. The two inputs for this system are the battery power and the incoming
RF messages which are passed through the RF transceiver Module and output the
outgoing RF messages. %
%
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/img/remoteBlockDiagram.png}
  \caption{Remote Target block diagram}
  \label{fig:remote_block_diag}
\end{figure}
%

The Mobile Cart subsystem block diagram, shown in Fig.
\ref{fig:mobile_block_diag}, is the most complex of the two subsystems. %
%
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
  \label{fig:mobile_block_diag}
\end{figure}
%

The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the
Li-Po works well with powering the embedded computer (BeagleBone Blue). The
power to the subsystem will be toggled by an on/off switch located on the
chassis of the robotic cart. The final input to the mobile cart subsystem is the
incoming RF signals. These incoming RF signals are passed to the direction
sensitive RF receivers which output the signals to the dual-direction
multiplexer. The dual-direction multiplexer then takes the four inputs from the
direction sensitive RF receivers and passes one output into the embedded
computer. Once the embedded computer gets these signals it can calculate the
localization and navigation algorithms and pass the information to the DC
motors.

@@

%----------------------------------------------------------------------
\section{System Components}
%----------------------------------------------------------------------

There are several components that are required for the mobile cart system.
Although some of these parts are available in the Bradley University laboratory,
other parts must be purchased. The parts that exist in the lab are listed in
\autoref{tab:Partslablist}. Also, \autoref{tab:Partslist} shows the list of
parts that were purchased. The parts compiled in the lists are the required
parts needed to build two smart robotic cart systems.

@@

\vspace*{12pt}
\noindent
The reflector array will be mounted on top of the cart with a stepper motor.
There are two reflector designs that were evaluated in this project. The first,
shown in Fig. \ref{fig:parabolodialReflector}, is a paraboloidal reflector which
maximizes the signal strength of the signals that come into the reflector
perpendicularly. Since the remote will be carried by the user, it is likely that
it will be positioned at a higher altitude than the reflector array. The
paraboloidal reflector design may not be able to pick up the signals from the
remote as well because of this. %
%
%
\begin{figure}
  \centering
  \begin{minipage}[t]{0.5\textwidth}
    \centering
    \includegraphics[height=2in]{figs/img/paraboloidalReflector}
    \captionsetup{width=\textwidth, justification=raggedright}
    \caption{Paraboloidal Reflector Model}
    \label{fig:parabolodialReflector}
  \end{minipage}
  \begin{minipage}[t]{0.4\textwidth}
    \centering
    \includegraphics[height=2in]{figs/img/parabolicReflector}
    \captionsetup{width=\textwidth, justification=raggedright}
    \caption{Combined Parabolic/Paraboloidal Reflector}
    \label{fig:parabolicReflector1}
  \end{minipage}
\end{figure}
%

To solve this problem, a combination parabolic/paraboloidal reflector was
designed, as shown in Fig. \ref{fig:parabolicReflector1}. The lower half of this
reflector is paraboloidal in shape to limit the signals coming from below. The
upper part of the reflector is strictly parabolic. This shape focuses the
signals in the horizontal plane, but allows signals from above to still be
received. The plan is to construct both of these reflector designs by 3D
printing the frames, then lining them with reflective foil tape. Both models
will then be tested to determine which design works better.

### 2021-05-01 parts/30-customized_parabolic_reflector_array.tex
Final report updates
Initial feedback from Dr. Miah

@@

%----------------------------------------------------------------------
\section{Reflector Construction}
%----------------------------------------------------------------------
With the recent advancements in 3D printing technology, it is not difficult to create an object with a parabolic shape. In this project, the reflector dishes were created using a 3D printer. The reflector array was designed to be modular, where the dishes, top plate, and bottom frame were printed separately. After printing, the dishes were lined with foil tape to provide the reflective surface to focus the signals onto the antenna of the XBee. A layer of foil tape was also placed on the top plate to provide a ground plane for the XBee. The parts were then fastened together using M3 screws and nuts.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

>>>>

\todo[inline]{Add an introductory paragraph (4/5 sentences maximum). What are
  you trying to talk about in this chapter, for example}

@@

%----------------------------------------------------------------------
\section{Reflector Construction}
%----------------------------------------------------------------------
With the recent advancements in 3D printing technology, it is not difficult to
create an object with a parabolic shape. In this project, the reflector dishes
were created using a 3D printer. The reflector array was designed to be modular,
where the dishes, top plate, and bottom frame were printed separately. After
printing, the dishes were lined with foil tape to provide the reflective surface
to focus the signals onto the antenna of the XBee. A layer of foil tape was also
placed on the top plate to provide a ground plane for the XBee. The parts were
then fastened together using M3 screws and nuts (Fig.
\ref{fig:reflectorConstruction}).
%
\begin{figure}
    \centering
    \includegraphics[width=3.5in]{figs/img/reflectorConstruction.jpg}
    \caption{Reflector Construction}
    \label{fig:reflectorConstruction}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:

### 2021-05-01 parts/40-algorithms.tex
Initial feedback from Dr. Miah

%======================================================================
\chapter{Algorithms}
\label{ch: Chapter4}
%======================================================================

%----------------------------------------------------------------------
\section{Robot Model}\label{sec:robotModel}
%----------------------------------------------------------------------
The robot used in this project was a differential drive mobile robot, which has two drive wheels and a caster wheel for balance. The robot turns by applying different speeds to the left and right wheels. As shown in Fig. \ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance between the wheels is $L$. The pose of the robot is given by the $x$-coordinate ($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in Fig. \ref{fig:robotPose}.
\begin{figure}
    \centering
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotGeometry.png}
        \caption{Robot Geometry}
        \label{fig:robotGeometry}
    \end{subfigure}%
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotPose.png}
        \caption{Robot Pose}
        \label{fig:robotPose}
    \end{subfigure}
    \caption{Robot Model Parameters}
    \label{fig:robotModelParameters}
\end{figure}

\vspace*{12pt}
\noindent
Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively). These speeds must be converted into left and right wheel speeds. The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively):
$$\omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}$$
$$\omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}$$
To control DC motors in this way, the relationship between duty cycle and angular speed must be determined. Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.

>>>>

%======================================================================
\chapter{Localization and Navigation}
\label{ch: Chapter4}
%======================================================================

\todo[inline]{Add an introductory paragraph. For example, ``In this Chapter, we
  illustrate localization and navigation algorithms for the mobile cart to operate in an
  indoor/outdoor environment. For that, we first model the proposed robotic cart
  as a differential drive mobile robot (DDMR). The position of the cart is then
  determined using a localization algorithm. $\ldots$''}

%----------------------------------------------------------------------
\section{Robot Model}\label{sec:robotModel}
%----------------------------------------------------------------------
The robot used in this project was a differential drive mobile robot, which has
two drive wheels and a caster wheel for balance. The robot turns by applying
different speeds to the left and right wheels. As shown in Fig.
\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance
between the wheels is $L$. The pose of the robot is given by the $x$-coordinate
($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in
Fig. \ref{fig:robotPose}. %
%
\begin{figure}
    \centering
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotGeometry.png}
        \caption{Robot Geometry}
        \label{fig:robotGeometry}
    \end{subfigure}%
    \begin{subfigure}{0.7\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/robotPose.png}
        \caption{Robot Pose}
        \label{fig:robotPose}
    \end{subfigure}
    \caption{Robot Model Parameters}
    \label{fig:robotModelParameters}
\end{figure}
%

Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively). These speeds must be converted into left and right wheel speeds. The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively):
$$\omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}$$
$$\omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}$$
To control DC motors in this way, the relationship between duty cycle and angular speed must be determined. Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.
